---
title: "DHE_relative_risk"
author: "Benjamin Young"
date: "17/03/2021"
output: html_document
---

```{r package loading, include = F}
library(tidyverse)
library(runjags)
library(rjags)
library(R2jags)
library(ggmcmc)
library(MCMCvis)
library(coda)
library(pairwiseCI)
library(gmodels)
```

```{r Data read in and prep, include = F}
read.csv("~/Documents/projects/DHE/manuscript/metadata/hdl.csv") %>%
  mutate(
    TIME = factor(
      .$Time_after_disease_exposure,
      c(
        "pre_exposure",
        "day_1",
        "day_2",
        "day_3",
        "day_4",
        "day_5",
        "day_6",
        "day_7",
        "day_8",
        "day_9",
        "day_10"
      )
    ),
    HEALTH = factor(.$HEALTH, c("healthy", "diseased", "dead"))
  ) %>% 
  na.omit() -> hdl

str(hdl)
#View(hdl)
```

```{r Remvoing pre exposure diseased}
hdl %>% 
  filter(TIME %in% c("pre_exposure"), 
         HEALTH %in% c("diseased", "dead")) %>% 
  column_to_rownames(var = "Frag_number") %>% 
  rownames() -> frag_num_filt

hdl %>% filter(!Frag_number %in% frag_num_filt) -> HDL
```


## Serratia and Disease Slurry RR Split by Ambient and Heat

```{r Serratia Ambient and Heat results}
HDL %>%
  dplyr::filter(D_treatment %in% c("s_m_placebo", "s_marcscens"), 
                TIME %in% c("day_10")) %>%
  dplyr::select(D_treatment, Tank_treatment, Genotype, TIME, HEALTH) %>%
  mutate(END_STATUS = case_when(
    HEALTH == "diseased" ~ "DISEASED", 
    HEALTH == "dead" ~ "DISEASED", 
    HEALTH == "healthy" ~ "HEALTHY"
  )) %>%
  group_by(D_treatment, Tank_treatment, Genotype, END_STATUS) %>% 
  dplyr::summarise(count = n()) %>% 
  ungroup() %>%
  complete(D_treatment, Tank_treatment, Genotype, END_STATUS, fill = list(count = 0)) -> ser_all

ser_all %>% 
  filter(Tank_treatment %in% c("ambient")) -> ser_ambient

ser_all %>% 
  filter(Tank_treatment %in% c("heat")) -> ser_heat

ser_ambient
ser_heat
```

```{r Disease slurry for ambient and heat}
HDL %>%
  dplyr::filter(D_treatment %in% c("disease_slurry", "placebo_slurry"), 
                TIME %in% c("day_10")) %>%
  dplyr::select(D_treatment, Tank_treatment, Genotype, TIME, HEALTH) %>%
  mutate(END_STATUS = case_when(
    HEALTH == "diseased" ~ "DISEASED", 
    HEALTH == "dead" ~ "DISEASED", 
    HEALTH == "healthy" ~ "HEALTHY"
  )) %>%
  group_by(D_treatment, Tank_treatment, Genotype, END_STATUS) %>% 
  dplyr::summarise(count = n()) %>% 
  ungroup() %>%
  complete(D_treatment, Tank_treatment, Genotype, END_STATUS, fill = list(count = 0)) -> slurry_all

slurry_all %>% 
  filter(Tank_treatment %in% c("ambient")) -> slurry_ambient

slurry_all %>% 
  filter(Tank_treatment %in% c("heat")) -> slurry_heat

slurry_ambient
slurry_heat
```

```{r OpenJags model}
write("model{
  for (i in 1:k) {
    #Prior
    a[i] ~ dbeta(1,1)
    c[i] ~ dbeta(1,1)
    
    # Likelihood
    h[i] ~ dbin(a[i],r[i])
    l[i] ~ dbin(c[i],m[i])
    RRISK[i] <- a[i]/c[i]
    OR[i] <- (a[i]/(1-a[i]))/(c[i]/(1-c[i]))
    lnOR[i] <- log(OR[i])
    ppos[i] <- step(OR[i]-1)
  }
}
",file="~/Documents/projects/DHE/manuscript/relative_risk/dhe_rr.txt")
```

h = total number ofexperimental corals with disease
r = total number of experimental corals
l = total number control corals with disease
m = total number of control corals

I think the best way to visualise this the ambient treatment and then then the heat treatments. 

```{r Making ambient and heat for Jags}
ambient <- list(k=8, 
                h = c(4,2,3,4,1,0,0,0), 
                r = c(5,5,4,5,5,5,5,5), 
                l = c(1,0,1,0,0,1,0,1), 
                m = c(5,5,5,5,5,5,5,5))

heat <- list(k=8, 
             h = c(5,4,3,5,2,4,3,0), 
             r = c(5,5,4,5,5,5,4,5), 
             l = c(0,1,2,0,0,0,1,2), 
             m = c(5,5,4,4,5,5,4,5))
```

```{r Running Jags Model}
N=8

Jags1<-jags(ambient,
            parameters.to.save=c("RRISK"),
            model.file="~/Documents/projects/DHE/manuscript/relative_risk/dhe_rr.txt",
            n.iter=10000, 
            n.burnin=1000, 
            n.thin=1, 
            n.chains=2)

Jags2<-jags(heat,
            parameters.to.save=c("RRISK"),
            model.file="~/Documents/projects/DHE/manuscript/relative_risk/dhe_rr.txt",
            n.iter=10000, 
            n.burnin=1000, 
            n.thin=1, 
            n.chains=2)

round(Jags1$BUGSoutput$summary,2)
round(Jags2$BUGSoutput$summary,2)
```

```{r Quick RR Plots with CI Intervals}
MCMCplot(Jags1, 
         params = 'RRISK', 
         ylim = c(0.01, 1000), ref_ovl = T)

MCMCplot(Jags2, 
         params = 'RRISK', 
         ylim = c(0.01, 1000), ref_ovl = T)
```

```{r Ambient Relative Risk and caterpillar plot}
S <- ggs(as.mcmc(Jags1))

# View(ggs(as.mcmc(Jags1)))
# ggs_caterpillar

S %>% 
  mutate(Genet = case_when(Parameter == "RRISK[1]" ~ "CN2 DS", 
                           Parameter == "RRISK[2]" ~ "CN4 DS",
                           Parameter == "RRISK[3]" ~ "HS1 DS",
                           Parameter == "RRISK[4]" ~ "ML2 DS",
                           Parameter == "RRISK[5]" ~ "CN2 SM",
                           Parameter == "RRISK[6]" ~ "CN4 SM",
                           Parameter == "RRISK[7]" ~ "HS1 SM",
                           Parameter == "RRISK[8]" ~ "ML2 SM"), 
         Tank_treatment = "Ambient") -> S_plot_ambient

#ggmcmc(S, plot=c("density", "running", "caterpillar"))

ggs_caterpillar(S %>% 
                  filter(!Parameter %in% c("deviance")), 
                sort = F, thick_ci = c(0.05, 0.95), 
                thin_ci = F) + 
  scale_x_log10(breaks = c(0.01,0.1,1,10,100,1000), 
                labels=c(0.01,0.1,1,10,100,1000), 
                limits = c(0.01,1000)) + 
  geom_vline(aes(xintercept = 1)) + 
  scale_y_discrete(limits = rev(levels(S$Parameter))) + 
  theme_bw()
```

```{r Heat Relative Risk and caterpillar plot}
S <- ggs(as.mcmc(Jags2))

S %>% 
  mutate(Genet = case_when(Parameter == "RRISK[1]" ~ "CN2 DS", 
                           Parameter == "RRISK[2]" ~ "CN4 DS",
                           Parameter == "RRISK[3]" ~ "HS1 DS",
                           Parameter == "RRISK[4]" ~ "ML2 DS",
                           Parameter == "RRISK[5]" ~ "CN2 SM",
                           Parameter == "RRISK[6]" ~ "CN4 SM",
                           Parameter == "RRISK[7]" ~ "HS1 SM",
                           Parameter == "RRISK[8]" ~ "ML2 SM"), 
         Tank_treatment = "Heat") -> S_plot_heat


#ggmcmc(S, plot=c("density", "running", "caterpillar"))

ggs_caterpillar(S %>% 
                  filter(!Parameter %in% c("deviance")), 
                sort = F, 
                thin_ci = F) + 
  scale_x_log10(breaks = c(0.01,0.1,1,10,100,1000), 
                labels=c(0.01,0.1,1,10,100,1000), 
                limits = c(0.01,1000)) + 
  geom_vline(aes(xintercept = 1)) + 
  scale_y_discrete(limits = rev(levels(S$Parameter))) + 
  theme_bw()
```

```{r Combining Results}
S_plot_ambient %>% 
  rbind(S_plot_heat) %>% 
  filter(!Parameter %in% c("deviance")) %>% 
  mutate(Genet_tank = paste0(.$Genet, .$Tank_treatment)) -> RR_combined
# View(RR_combined)
```

```{r Getting median and CI for ggplot}
ggmcmc::ci(S_plot_ambient, thick_ci = c(0.05, 0.95)) %>% 
  rbind(ggmcmc::ci(S_plot_heat, thick_ci = c(0.05, 0.95))) %>% 
  filter(!Parameter %in% c("deviance")) %>% 
  mutate(Genet = as.factor(Genet), 
         Tank_treatment = as.factor(Tank_treatment), 
         GENET = fct_relevel(Genet, "CN2 DS", "CN4 DS", "HS1 DS", "ML2 DS", 
                             "CN2 SM", "CN4 SM", "HS1 SM", "ML2 SM")) -> RR_ci_ggplot

str(RR_ci_ggplot)
```

```{r RR plot using GGplot, fig.width = 6, fig.height=7}
ggplot(data = RR_ci_ggplot,
       aes(x = median, y = GENET, color = Tank_treatment)) +
  geom_point(position = position_dodge(width=0.7), 
             size = 2) +
  geom_linerange(aes(xmin = Low, xmax = High), 
                 position = position_dodge(width=0.7)) +
    scale_x_log10(
    breaks = c(0.01, 0.1, 1, 10, 100, 1000),
    labels = c(0.01, 0.1, 1, 10, 100, 1000),
    limits = c(0.01, 1000)
  ) + 
  theme_bw() + 
  geom_vline(xintercept = 1, 
             size = 0.25) + 
  geom_hline(yintercept = 4.5, 
             linetype = "dotted") +
  scale_color_manual(values = c("blue3", "orangered2")) + 
  scale_y_discrete(limits = rev)
```

Testing Relative Risks due to tank treatment
Methods following - https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1125071/ 

```{r Pvalue for each genet RR for disease due to treatment}
RR_ci_ggplot %>% 
  mutate(logRR = log(median), 
         loghigh = log(High), 
         loglow = log(Low), 
         width = abs(loglow - loghigh),
         se = width/(2*1.96)) %>%
  dplyr::select(7:14, - GENET) %>% View()
  pivot_wider(names_from = Tank_treatment , values_from = 3:7) %>% 
  mutate(logRR_dif = logRR_Ambient - logRR_Heat, 
         SE_dif = sqrt((se_Ambient^2)+(se_Heat^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) -> genet_inoc_temp_RR_signif_res
View(genet_inoc_temp_RR_signif_res)
```

```{r Pvalue for each genet RR for disease due to treatment}
RR_ci_plot_2 %>% 
  mutate(logRR = log(median), 
         loghigh = log(High), 
         loglow = log(Low), 
         width = abs(loglow - loghigh),
         se = width/(2*1.96)) %>%
  dplyr::select(7:15, -GENET, -Genet, genet_alone) %>%
  pivot_wider(names_from = Dtreatment , values_from = 3:7) %>% 
  mutate(logRR_dif = logRR_Serratia - logRR_Slurry, 
         SE_dif = sqrt((se_Serratia^2)+(se_Slurry^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) -> dis_inoc_genet_grouped_res
View(dis_inoc_genet_grouped_res)
```

## Relative Risk for Tank treatments Combined

```{r Serratia Ambient and Heat results, include = F}
HDL %>%
  dplyr::filter(D_treatment %in% c("s_m_placebo", "s_marcscens"), 
                TIME %in% c("day_10")) %>%
  dplyr::select(D_treatment, Tank_treatment, Genotype, TIME, HEALTH) %>%
  mutate(END_STATUS = case_when(
    HEALTH == "diseased" ~ "DISEASED", 
    HEALTH == "dead" ~ "DISEASED", 
    HEALTH == "healthy" ~ "HEALTHY"
  )) %>%
  group_by(D_treatment, Genotype, END_STATUS) %>% 
  dplyr::summarise(count = n()) %>%
  ungroup() %>%
  complete(D_treatment, Genotype, END_STATUS, fill = list(count = 0)) -> ser_all_geno
```

```{r Disease slurry for ambient and heat, include = F}
HDL %>%
  dplyr::filter(D_treatment %in% c("disease_slurry", "placebo_slurry"), 
                TIME %in% c("day_10")) %>%
  dplyr::select(D_treatment, Tank_treatment, Genotype, TIME, HEALTH) %>%
  mutate(END_STATUS = case_when(
    HEALTH == "diseased" ~ "DISEASED", 
    HEALTH == "dead" ~ "DISEASED", 
    HEALTH == "healthy" ~ "HEALTHY"
  )) %>%
  group_by(D_treatment, Genotype, END_STATUS) %>% 
  dplyr::summarise(count = n()) %>% 
  ungroup() %>%
  complete(D_treatment, Genotype, END_STATUS, fill = list(count = 0)) -> slurry_all_geno
```

```{r OpenJags model}
write("model{
  for (i in 1:k) {
    #Prior
    a[i] ~ dbeta(1,1)
    c[i] ~ dbeta(1,1)
    
    # Likelihood
    h[i] ~ dbin(a[i],r[i])
    l[i] ~ dbin(c[i],m[i])
    RRISK[i] <- a[i]/c[i]
    OR[i] <- (a[i]/(1-a[i]))/(c[i]/(1-c[i]))
    lnOR[i] <- log(OR[i])
    ppos[i] <- step(OR[i]-1)
  }
}
",file="~/Desktop/DHE_RR_geno.txt")
```

k = number of groups (here 4 genos, with tank temp = 8)
h = total number of experimental corals with disease
r = total number of experimental corals
l = total number control corals with disease
m = total number of control corals

I think the best way to visualise this the ambient treatment and then then the heat treatments. 

```{r Making ambient and heat for Jags}
serratia <- list(k=4, 
                h = c(3,4,3,0), 
                r = c(10,10,9,10), 
                l = c(0,1,1,3), 
                m = c(10,10,9,10))

slurry <- list(k=4, 
             h = c(9,6,6,9), 
             r = c(10,10,8,10), 
             l = c(1,1,3,0), 
             m = c(10,10,9,9))
```

```{r Running Jags Model}
N=4

Jags_Ser<-jags(serratia,
            parameters.to.save=c("RRISK"),
            model.file="~/Desktop/DHE_RR_geno.txt",
            n.iter=10000, 
            n.burnin=1000, 
            n.thin=1, 
            n.chains=2)

Jags_Slu<-jags(slurry,
            parameters.to.save=c("RRISK"),
            model.file="~/Desktop/DHE_RR_geno.txt",
            n.iter=10000, 
            n.burnin=1000, 
            n.thin=1, 
            n.chains=2)

round(Jags_Ser$BUGSoutput$summary,2)
round(Jags_Slu$BUGSoutput$summary,2)
```

```{r Quick RR Plots with CI Intervals, echo = F}
MCMCplot(Jags_Ser, 
         params = 'RRISK', 
         ylim = c(0.01, 1000), ref_ovl = T)

MCMCplot(Jags_Slu, 
         params = 'RRISK', 
         ylim = c(0.01, 1000), ref_ovl = T)
```

```{r Ambient Relative Risk and caterpillar plot, echo = F}
S_slu <- ggs(as.mcmc(Jags_Slu))

#View(ggs(as.mcmc(Jags_Slu)))
ggs_caterpillar

S_slu %>% 
  mutate(Genet = case_when(Parameter == "RRISK[1]" ~ "CN2 DS", 
                           Parameter == "RRISK[2]" ~ "CN4 DS",
                           Parameter == "RRISK[3]" ~ "HS1 DS",
                           Parameter == "RRISK[4]" ~ "ML2 DS"),
         Dtreatment = "Slurry") -> S_plot_slu

#ggmcmc(S, plot=c("density", "running", "caterpillar"))

ggs_caterpillar(S_slu %>% filter(!Parameter %in% c("deviance")), sort = F, thick_ci = c(0.05, 0.95), thin_ci = F) + 
  scale_x_log10(breaks = c(0.01,0.1,1,10,100,1000), labels=c(0.01,0.1,1,10,100,1000), limits = c(0.01,1000)) + 
  geom_vline(aes(xintercept = 1)) + 
  scale_y_discrete(limits = rev(levels(S_slu$Parameter))) + 
  theme_bw()
```

```{r Heat Relative Risk and caterpillar plot, echo = F}
S_ser <- ggs(as.mcmc(Jags_Ser))

S_ser %>% 
  mutate(Genet = case_when(Parameter == "RRISK[1]" ~ "CN2 SM", 
                           Parameter == "RRISK[2]" ~ "CN4 SM",
                           Parameter == "RRISK[3]" ~ "HS1 SM",
                           Parameter == "RRISK[4]" ~ "ML2 SM"), 
         Dtreatment = "Serratia") -> S_plot_ser


#ggmcmc(S, plot=c("density", "running", "caterpillar"))

ggs_caterpillar(S_ser %>% filter(!Parameter %in% c("deviance")), sort = F, thin_ci = F) + 
  scale_x_log10(breaks = c(0.01,0.1,1,10,100,1000), labels=c(0.01,0.1,1,10,100,1000), limits = c(0.01,1000)) + 
  geom_vline(aes(xintercept = 1)) + 
  scale_y_discrete(limits = rev(levels(S_ser$Parameter))) + 
  theme_bw()
```

```{r Combining Results, include = F}
S_plot_ser %>% 
  rbind(S_plot_slu) %>% 
  filter(!Parameter %in% c("deviance")) -> RR_combined_geno
# View(RR_combined)
```

```{r Getting median and CI for ggplot, include = F}
ggmcmc::ci(S_plot_ser, thick_ci = c(0.05, 0.95)) %>% 
  rbind(ggmcmc::ci(S_plot_slu, thick_ci = c(0.05, 0.95))) %>% 
  filter(!Parameter %in% c("deviance")) %>%
  mutate(Genet = as.factor(Genet),
         GENET = fct_relevel(Genet, "CN2 DS", "CN4 DS", "HS1 DS", "ML2 DS", 
                             "CN2 SM", "CN4 SM", "HS1 SM", "ML2 SM")) -> RR_ci_ggplot

RR_ci_ggplot %>% 
  mutate(genet_alone = case_when(GENET == "CN2 DS" ~ "CN2", 
                                 GENET == "CN2 SM" ~ "CN2",
                                 GENET == "CN4 DS" ~ "CN4", 
                                 GENET == "CN4 SM" ~ "CN4",
                                 GENET == "HS1 DS" ~ "HS1", 
                                 GENET == "HS1 SM" ~ "HS1",
                                 GENET == "ML2 DS" ~ "ML2", 
                                 GENET == "ML2 SM" ~ "ML2")) -> RR_ci_plot_2
# str(RR_ci_ggplot)
#View(RR_ci_ggplot)
```

```{r RR plot using GGplot, echo = F}
ggplot(data = RR_ci_ggplot,
       aes(x = median, y = GENET)) +
  geom_point(position = position_dodge(width=0.7), 
             size = 2) +
  geom_linerange(aes(xmin = Low, xmax = High), 
                 position = position_dodge(width=0.7)) +
    scale_x_log10(
    breaks = c(0.01, 0.1, 1, 10, 100, 1000),
    labels = c(0.01, 0.1, 1, 10, 100, 1000),
    limits = c(0.01, 1000)
  ) + 
  theme_bw() + 
  geom_vline(xintercept = 1, 
             size = 0.25) + 
  geom_hline(yintercept = 4.5, 
             linetype = "dotted") +
  scale_color_manual(values = c("darkgrey", "black")) + 
  scale_y_discrete(limits = rev)
```

```{r RR plot using GGplot, echo = F, fig.width = 5.5, fig.height=7}
ggplot(data = RR_ci_plot_2,
       aes(x = median, y = genet_alone, colour = Dtreatment)) +
  geom_point(position = position_dodge(width = 0.7),
             size = 2) +
  geom_linerange(aes(xmin = Low, xmax = High),
                 position = position_dodge(width = 0.7)) +
  scale_x_log10(
    breaks = c(0.01, 0.1, 1, 10, 100, 1000),
    labels = c(0.01, 0.1, 1, 10, 100, 1000),
    limits = c(0.01, 1000)
  ) +
  theme_bw() +
  geom_vline(xintercept = 1,
             size = 0.25) +
  scale_color_manual(values = c("plum1", "aquamarine3")) +
  scale_y_discrete(limits = rev)
```

Testing Relative Risks due to tank treatment
Methods following - https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1125071/ 

```{r Pvalue for each genet RR for disease due to treatment}
RR_ci_ggplot %>% 
  mutate(logRR = log(median), 
         loghigh = log(High), 
         loglow = log(Low), 
         width = abs(loglow - loghigh),
         se = width/(2*1.96)) %>% 
  mutate(Genotype = case_when(GENET == "CN2 DS" ~ "CN2", 
                              GENET == "CN2 SM" ~ "CN2", 
                              GENET == "CN4 DS" ~ "CN4", 
                              GENET == "CN4 SM" ~ "CN4", 
                              GENET == "ML2 DS" ~ "ML2", 
                              GENET == "ML2 SM" ~ "ML2", 
                              GENET == "HS1 DS" ~ "HS1", 
                              GENET == "HS1 SM" ~ "HS1")) %>% 
  dplyr::select(8:15, - GENET) %>%
  pivot_wider(names_from = Genotype , values_from = 2:6) %>% 
  mutate(logRR_dif = logRR_CN2 - logRR_CN4, ## CN2 and CN4
         SE_dif = sqrt((se_CN2^2)+(se_CN4^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN2_CN4 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>%
  mutate(logRR_dif = logRR_CN2 - logRR_HS1, ## CN2 and HS1
         SE_dif = sqrt((se_CN2^2)+(se_HS1^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN2_HS1 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_CN2 - logRR_ML2, ## CN2 and ML2
         SE_dif = sqrt((se_CN2^2)+(se_ML2^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN2_ML2 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_CN4 - logRR_HS1, ## CN4 AND HS1
         SE_dif = sqrt((se_CN4^2)+(se_HS1^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN4_HS1 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_CN4 - logRR_ML2, # CN4 AND ML2
         SE_dif = sqrt((se_CN4^2)+(se_ML2^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_ML2_CN4 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_ML2 - logRR_HS1, # ML2 AND HS1
         SE_dif = sqrt((se_ML2^2)+(se_HS1^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_ML2_HS1 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) -> geno__inor_RR_res

View(geno__inor_RR_res)
geno__inor_RR_res %>%
  dplyr::select(1, 27:32) %>% View()
```


## Testing Combined Disease Inoculations for Genet

```{r Genet Results, include = F}
HDL %>%
  dplyr::filter(TIME %in% c("day_10")) %>%
  dplyr::select(D_treatment, Tank_treatment, Genotype, TIME, HEALTH) %>%
  mutate(
    END_STATUS = case_when(
      HEALTH == "diseased" ~ "DISEASED",
      HEALTH == "dead" ~ "DISEASED",
      HEALTH == "healthy" ~ "HEALTHY"),
    Inoc_type = case_when(D_treatment == "disease_slurry" ~ "pathogenic", 
                          D_treatment == "s_marcscens" ~ "pathogenic", 
                          D_treatment == "placebo_slurry" ~ "control",
                          D_treatment == "s_m_placebo" ~ "control"),
  ) %>% 
  group_by(Inoc_type, Genotype, END_STATUS) %>%
  dplyr::summarise(count = n()) %>%
  ungroup() %>%
  complete(Inoc_type, Genotype, END_STATUS, fill = list(count = 0)) -> genet_health

# View(genet_health)
```

```{r OpenJags model}
write("model{
  for (i in 1:k) {
    #Prior
    a[i] ~ dbeta(1,1)
    c[i] ~ dbeta(1,1)
    
    # Likelihood
    h[i] ~ dbin(a[i],r[i])
    l[i] ~ dbin(c[i],m[i])
    RRISK[i] <- a[i]/c[i]
    OR[i] <- (a[i]/(1-a[i]))/(c[i]/(1-c[i]))
    lnOR[i] <- log(OR[i])
    ppos[i] <- step(OR[i]-1)
  }
}
",file="~/Desktop/DHE_RR_geno.txt")
```

k = number of groups (here 4 genos)
h = total number of experimental corals with disease
r = total number of experimental corals
l = total number control corals with disease
m = total number of control corals

I think the best way to visualise this the ambient treatment and then then the heat treatments. 

Order is 
CN2, CN4, HS1, ML2

```{r Making JAGS for just genet, include = F}
genet <- list(k=4, 
                h = c(12,10,9,9), 
                r = c(20,20,17,20), 
                l = c(1,2,4,3), 
                m = c(20,20,18,19))
```

```{r Running Jags Model for genet only, include = F}
N=4

Jags_gen<-jags(genet,
            parameters.to.save=c("RRISK"),
            model.file="~/Desktop/DHE_RR_geno.txt",
            n.iter=10000, 
            n.burnin=1000, 
            n.thin=1, 
            n.chains=2)

round(Jags_gen$BUGSoutput$summary,2)
```

```{r Quick RR Plots with CI Intervals, echo = F}
MCMCplot(Jags_gen, 
         params = 'RRISK', 
         ylim = c(0.01, 1000), ref_ovl = T)
```

```{r Ambient Relative Risk and caterpillar plot}
S_gen <- ggs(as.mcmc(Jags_gen))

#View(ggs(as.mcmc(Jags_Slu)))
# ggs_caterpillar

S_gen %>% 
  mutate(Genet = case_when(Parameter == "RRISK[1]" ~ "CN2", 
                           Parameter == "RRISK[2]" ~ "CN4",
                           Parameter == "RRISK[3]" ~ "HS1",
                           Parameter == "RRISK[4]" ~ "ML2")) -> S_plot_gen

#ggmcmc(S, plot=c("density", "running", "caterpillar"))

ggs_caterpillar(
  S_gen %>% filter(!Parameter %in% c("deviance")),
  sort = F,
  thick_ci = c(0.05, 0.95),
  thin_ci = F
) +
  scale_x_log10(
    breaks = c(0.01, 0.1, 1, 10, 100, 1000),
    labels = c(0.01, 0.1, 1, 10, 100, 1000),
    limits = c(0.01, 1000)
  ) +
  geom_vline(aes(xintercept = 1)) +
  scale_y_discrete(limits = rev(levels(S_gen$Parameter))) +
  theme_bw()
```

```{r Getting median and CI for ggplot}
ggmcmc::ci(S_plot_gen, thick_ci = c(0.05, 0.95)) %>% 
  filter(!Parameter %in% c("deviance")) %>%
  mutate(Genet = as.factor(Genet),
         GENET = fct_relevel(Genet, "CN2", "CN4", "HS1", "ML2")) -> RR_ci_ggplot

# str(RR_ci_ggplot)
View(RR_ci_ggplot)
```

```{r RR plot using GGplot, fig.width=5.5, fig.height=7}
ggplot(data = RR_ci_ggplot,
       aes(x = median, y = GENET, color = GENET)) +
  geom_point(position = position_dodge(width=0.7), 
             size = 2) +
  geom_linerange(aes(xmin = Low, xmax = High), 
                 position = position_dodge(width=0.7)) +
    scale_x_log10(
    breaks = c(0.01, 0.1, 1, 10, 100, 1000),
    labels = c(0.01, 0.1, 1, 10, 100, 1000),
    limits = c(0.01, 1000)
  ) + 
  theme_bw() + 
  geom_vline(xintercept = 1, 
             size = 0.25) + 
  scale_color_manual(values = c("wheat3", "navy" ,"springgreen4", "grey60")) + 
  scale_y_discrete(limits = rev)
```

Testing Relative Risks due to tank treatment
Methods following - https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1125071/ 

```{r Pvalue for each genet RR for disease due to treatment}
RR_ci_ggplot %>% 
  mutate(logRR = log(median), 
         loghigh = log(High), 
         loglow = log(Low), 
         width = abs(loglow - loghigh),
         se = width/(2*1.96)) %>% 
  dplyr::select(8:13) %>% 
  pivot_wider(names_from = GENET , values_from = 2:6) %>%
  mutate(logRR_dif = logRR_CN2 - logRR_CN4, ## CN2 and CN4
         SE_dif = sqrt((se_CN2^2)+(se_CN4^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN2_CN4 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>%
  mutate(logRR_dif = logRR_CN2 - logRR_HS1, ## CN2 and HS1
         SE_dif = sqrt((se_CN2^2)+(se_HS1^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN2_HS1 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_CN2 - logRR_ML2, ## CN2 and ML2
         SE_dif = sqrt((se_CN2^2)+(se_ML2^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN2_ML2 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_CN4 - logRR_HS1, ## CN4 AND HS1
         SE_dif = sqrt((se_CN4^2)+(se_HS1^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_CN4_HS1 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_CN4 - logRR_ML2, # CN4 AND ML2
         SE_dif = sqrt((se_CN4^2)+(se_ML2^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_ML2_CN4 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) %>% 
  mutate(logRR_dif = logRR_ML2 - logRR_HS1, # ML2 AND HS1
         SE_dif = sqrt((se_ML2^2)+(se_HS1^2)), 
         CI_dif_pos = logRR_dif + (1.96*SE_dif), 
         CI_dif_neg = logRR_dif - (1.96*SE_dif), 
         Interaction = logRR_dif/SE_dif, 
         pvalue_ML2_HS1 = 2*pnorm(abs(Interaction), mean = 0, sd = 1, lower.tail = F)) -> geno_results

geno_results %>%
  dplyr::select(26:31) %>% View()
```

